Exposing Disputed Statements on the Web

### 2009-03-19 papers/uist_thinklink/thinklink.tex
More work on related work

@@

\subsection{Tagging and Annotating}

Video Annotation~\cite{Diakopoulos2008}

Tagging~\cite{Marlow2006}. Tagomizer~\cite{Park2007}. Reasons for choices of tags~\cite{Sen2006}. Tagging Roles~\cite{Muller2008}.

SpinSpotter\footnote{http://spinspotter.com}. ClipMarks\footnote{http://clipmarks.com}, Diigo~\footnote{http://diigo.com}, Stickis\footnote{http://stickis.com}.

How to Personalize the Web~\cite{Barrett1997}.

\subsection{Clipping}

ScratchPad~\cite{Gotz2007}. Internet Scrapbook~\cite{Sugiura1998}. Reverse Linking~\cite{Yesilada2007}. Hunter Gatherer~\cite{2002}. Dontcheva~\cite{Dontcheva2007a}.

\subsection{Semantic Web}

Nobody is going to mark up their own web page as being wrong.

@@

Think Link is very influenced by wikis like Wikipedia~\cite{wikipedia}. Like Think Link, wikis allow users to find information organized by topic rather than author and allow users to collaborate together to bring together all the best information about a topic. Wikipedia's greatest strength is arguably also its greatest weakness. Since anyone can edit Wikipedia, there is always the danger that information one reads may be incorrect~\cite{wikifalse}. Several projects have attempted to address this problem by tracking sources of edits~\cite{wikicorrect,wikicorrect2,wikicorrect3}, but it is difficult to remove the problem entirely. While good Wikipedia articles will often include references to sources for their claims, following all sources to check up all claims can be laborious. Think Link tries to avoid this problem by linking claims back to the original sources that made these claims. Users can thus use the known trustworthiness of the original sources to judge the reliability of a claim.

When a topic is heavily politicized, Wikipedia can be subject to edit wars in which people who hold one opinion delete opinions held by the other side~\cite{wikicorrect3}, making it difficult for the community to collaborate together to produce a document that is both comprehensive and unbiased. Think Link attempts to avoid this problem by taking an ``append-only, collaborative filtering'' approach. A user cannot remove claims that they disagree with\footnote{With special exceptions for dealing with spam and abuse}. Instead all they can do is vote against them, and connect them to claims that provide opposing evidence.

Another key difference between Think Link and a wiki is that Think Link pulls the whole web into its graph of connected claims. A user can use Think Link to investigate claims they read on arbitrary web sites, without having to restrict their browsing to a single wiki site.

SpinSpotter~\cite{spinspotter} shares Think Link's goal of allowing users to identify misleading and inaccurate information on web pages that they read. If a user sees a section of text that they think is misleading then they can mark it up, causing it to be highlighted when other users view the same page. While Think Link and SpinSpotter both share the goal of letting users mark up snippets that may be inaccurate, they differ in what they let users find out about such snippets. SpinSpotter allows users to give a textual description of why the snippet is spin and a suggested edit that would make it more accurate. Think Link instead connects the snippet to its global claim graph, allowing users to quickly access evidence for and against the truth of the claim. There is also a difference in the nature of what SpinSpotter and Think Link expect users to mark up. Think Link is interested in evaluating the truth of factual claims, while SpinSpotter also interested in identifying biased phrases (e.g. ``tree hugger'').

Other web annotation systems such as ShiftSpace.org, Stickis.com, SharedCopy.com, and Diigo.com allow people to add their own annotations to existing web pages and view annotations written by other people. Common annotations include commenting on perceived inaccuracies, highlighting interesting passages, or linking to other relevant documents. More generally, tools like WBI~\cite{personalweb} and Mash Maker~\cite{mashmaker} allow arbitrary changes to be made to web pages. We are not aware of any such system that links web pages to a graph of factual claims.

Web clipping tools such as Google Notebook, Scrapbook~\cite{scrapbook}, and Zotero.org allow one to gather and organize interesting from web pages. Many web clipping tools are also web annotation systems. These tools are designed for gathering and sharing interesting information, rather than for identifying the claims being made, or allowing users to navigate to related claims being made on other sites.

In Vannevar Bush's seminal MEMEX article~\cite{memex} he proposed an architecture in which links between documents were established by readers, according to the associations between them. As Bush says: ``It is exactly as though the physical items had been gathered together from widely separated sources and bound together to form a new book''. Several more recent systems have allowed user to add links to existing pages. ENQUIRE~\cite{weavingtheweb} and TrackBack~\cite{trackback} have bidirectional links, allowing one to see the sites that link to a page as well as those that link from it. Everything2.com links each page to the most popular pages that users viewed at the same time. Think Link's key difference from this work is that it imposes an additional layer of structure, identifying the factual claims that snippets are making and allowing users to browse this graph, rather than just allowing users to specify links between pages.

@@

We would like to think Allison Woodruff, Tye Rattenbury, and all our user study participants for all their help during the design of Think Link. Think Link uses icons from the free FamFamFam Silk~\cite{silkicons} collection.

\bibliography{refs}

>>>>

In attempt to unify the different argumentation tools being developed, several interchange formats have been proposed~\cite{Rahwan2007a,McGinnis2007} to allow different web argumentation tools to share descriptions of contentious issues.

@@

\subsection{Tagging, Clipping, and Annotating}

Tagging Systems~\cite{Marlow2006,Golder2006} allow users to collect and organize information by associating it with an ad-hoc collection of tags. Notable tagging systems include del.icio.us\footnote{http:\\del.icio.us} which uses tags to organize web pages, and Flickr\footnote{http://flickr.com} which associates tags with photos.

Some tagging tools also do clipping. Clipping tools such as Internet Scrapbook~\cite{Sugiura19998}, Hunter Gatherer~\cite{2002}, ScratchPad~\cite{Gotz2007}, ClipMarks\footnote{http://clipmarks.com}, and Diigo\footnote{http://diigo.com} allow users to collect text snippets from web pages, tag them, and share them with friends. In many cases, a tagging or clipping system will also allow users who are looking at a tagged or clipped object to see the tags that other users have associated with it, or highlight the parts of a document that have been clipped.

Several tools allow users to mark up content that is considered to controversial. Videolyzer~\cite{Diakopoulos2008} allows users to annotate and comment on political videos with accompanying textual transcriptions. A user can mark up a section of video for bias, accuracy, or rhetorical technique. Comments can include references to external sources that back up the argument being made.

SpinSpotter\footnote{http://spinspotter.com} allows a user to highlight snippets of text that contain spin or bias and either describe why the text is biased, or rewrite the text in an unbiased way. While SpinSpotter and Think Link share a goal of drawing user attention to biased or inaccurate information, they do so in a different way. SpinSpotter annotates a snippet with an annotation specific to that particular snippet of text, while Think Link treats a snippet as being an instance of a shared contentious claim, and links all snippets identified as making that claim to a shared graph node linking to other information about that claim.

\subsection{Augmented Web Navigation}

Several tools layer an alternative navigation graph over information on the web. TextRunner~\cite{Etzioni2008} looks for instances of subject-verb-object triples on web pages and connects these together as a graph in which objects are linked by statements made about them on different web pages.

Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books. This ``linking of quotations'' is similar in spirit to the linking of claims in Think Link.

% Tagging~\cite{Marlow2006}. Tagomizer~\cite{Park2007}. Reasons for choices of tags~\cite{Sen2006}. Tagging Roles~\cite{Muller2008}. 
% 
% SpinSpotter\footnote{http://spinspotter.com}. ClipMarks\footnote{http://clipmarks.com}, Diigo~\footnote{http://diigo.com}, Stickis\footnote{http://stickis.com}.
% 
% How to Personalize the Web~\cite{Barrett1997}.

% \subsection{Clipping}
% 
% ScratchPad~\cite{Gotz2007}. Internet Scrapbook~\cite{Sugiura1998}. Reverse Linking~\cite{Yesilada2007}. Hunter Gatherer~\cite{2002}. Dontcheva~\cite{Dontcheva2007a}.

% \subsection{Semantic Web}
% 
% Nobody is going to mark up their own web page as being wrong.

@@

@@

We would like to think Allison Woodruff, Tye Rattenbury, and all our user study participants for all their help during the design of Think Link. Think Link uses icons from the free FamFamFam Silk\footnote{http:\\famfamfam.com} collection.

\todo{Sort out bad references}
\bibliography{refs}
